---
title: "Chicago_crime"
author: "Carson"
date: "December 22, 2018"
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Load Crime Data for Web
Data sets containing crimes reported since 2015 will be downloaded from the City of Chicago's website; 'data.cityofchicago.org/Public-Safety' 
```{r Load Data, message=FALSE}
library(leaflet)
library(dplyr)
library(data.table)

crimeDf <- read.csv(url("https://data.cityofchicago.org/api/views/vwwp-7yr9/rows.csv?accessType=DOWNLOAD&bom=true&format=true"))
crimeDf <- as.data.table(crimeDf)
```


## Group Longitude and Latiture data points
Since the data set records Long & Lat to a level of specificity that does not allow us to create substantial enough groups to identify patterns from, we will instead bin our continuous longitude and latitude data points by '0.1'.  
```{r, echo=FALSE}
summary(crimeDf$Latitude)

summary(crimeDf$Longitude)
```

```{r pressure, echo=TRUE}
binsLat <- seq(41.6, 42.1, .10)
latLabels <- seq(41.6, 42, .1)
crimeDf$lat_bin <- as.numeric(as.character(cut(crimeDf$Latitude, binsLat, labels=latLabels)))

binsLong <- seq(-88, -87.5, .1)
longLabels <- seq(-88, -87.6, .1)
crimeDf$long_bin <- as.numeric(as.character(cut(crimeDf$Longitude, binsLong, labels=longLabels)))
```


## Summarize Data 
Summarize the volume of arrests made by our grouped longitude and latitude data points.
```{r Summarize Data, echo=FALSE, include=FALSE}
library(data.table)

crimeSumm <- as.data.table(crimeDf)[(!is.na(crimeDf$lat_bin) & !is.na(crimeDf$long_bin)),
                     list(
                       total_arrests = length(Arrest == TRUE)
                     ),
                     by = c("lat_bin", "long_bin")]
```

```{r, echo=FALSE}
print(crimeSumm)
```

## Create Geospatial Map 
This map will vary the size of the circles made based upon arrests made within our grouped longitude and latitude areas.
```{r}
library(dplyr)
library(leaflet)

crimeSumm %>% 
  leaflet() %>%
  addTiles() %>%
  addCircles(lng=crimeSumm$long_bin,
             lat=crimeSumm$lat_bin,
             weight = 1, 
             radius = sqrt(crimeSumm$total_arrests) * 30)
```